Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
anotaciones

The other application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, is a classical molecular dynamics simulator that can be applied at the atomic, meso, or continuum scale. 
From the implementation perspective, this multi-process application employs at least one GPU to host its processes, but can benefit from the use of multiple GPUs.
The Figure shows that running this application using remote GPUs does not offer any advantage in front of original CUDA. 
Furthermore, for the execution on remote GPUs, can be seen a little difference between both networks, the ``High'' network performs worse than ``10 Gb'' network.
Thus, if we compare the results of a LAMMPS execution with a larger problem (see Figure), while CUDA performs better, the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks what means that the transfers are making the interconnection network the bottleneck, and enlarging the problem size
pays off the drawback of a slow network.

\begin{figure}[htb]
\centering
\subfigure[first]{%
\includegraphics[width=0.455\linewidth]{images/lammps100.png}
\label{subfig:lammps1}}
\quad
\subfigure[second]{%
\includegraphics[width=0.455\linewidth]{images/lammps2000.png}
\label{subfig:lammps2}}
\caption{Execution time of LAMMPS}
\label{fig:lammps}
\end{figure}

@@

\section{\uppercase{GPGPU Shared Service in OpenStack}}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

>>>>

The other application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, is a classical molecular dynamics simulator that can be applied at the atomic, meso, or continuum scale. 
From the implementation perspective, this multi-process application employs at least one GPU to host its processes, but can benefit from the use of multiple GPUs.
The Figure shows that running this application using remote GPUs does not offer any advantage in front of original CUDA. 
Furthermore, for the execution on remote GPUs, can be seen a little difference between both networks, the ``High'' network performs worse than ``10 Gb'' network.
Thus, if we compare the results of a LAMMPS execution with a larger problem (see Figure), although CUDA continues performing better, the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks what means that the transfers are making the interconnection network the bottleneck, and enlarging the problem size
pays off the drawback of a slower network.

\begin{figure}[htb]
\centering
\subfigure[first]{%
\includegraphics[width=\linewidth]{images/lammps100.png}
\label{subfig:lammps1}}
\quad
\subfigure[second]{%
\includegraphics[width=\linewidth]{images/lammps2000.png}
\label{subfig:lammps2}}
\caption{Execution time of LAMMPS}
\label{fig:lammps}
\end{figure}

@@

\section{\uppercase{GPGPU Shared Service in OpenStack}}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.

Version de open stack con la que se trabaja y tipo de instalacion ya que está toda en un nodo...

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/os-orig.png}
  \caption{Openstack Architecture}
  \label{fig:os-orig}
\end{figure}

\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.
